COG-ED Manuscript

### 2021-10-20 06_Paper/COG-ED/Manuscript.Rmd
tried to fix AUC sorted
Function ignores argument

  h3c_data <- data.frame(subject = character(), auc_sv = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = TRUE))
    h3c_data <- rbind(h3c_data, newdata)

@@

@@

  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))

@@

However, when only taking the AUC of the mental and the AUC of the effort subscale of the NASA-TLX into account, it explained variance in NFC scores beyond SVs (`r apa_print(hypothesis3c)$statistic$modelfit$r2`, `r apa_print(hypothesis3c)$estimate$modelfit$r2`).

>>>>

  h3c_data <- data.frame(subject = character(), auc_sv_sorted = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv_sorted = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = TRUE))
    h3c_data <- rbind(h3c_data, newdata)

@@

  h3_data <- merge(h3_data, h3c_data)

  # remove temporary variable

  remove(h3c_data)

@@

  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv_sorted))

@@
